A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-22 manuscript.Rmd
add minimal setup

# The lifecycle of an open research project

<!-- many small steps archive reproducibility -->

## Setup

@@

We assume that you have already installed R and RStudio (if not check the installation guide).
Additionally, you'll need the [`repro`-package](https://github.com/aaronpeikert/repro):

@@

@@

```{r}
check_github()
```

>>>>

# Setup

@@

We assume that you have already installed R and RStudio (if not check the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/master/install.md", "installation guide")`).
Additionally, you'll need the [`repro`-package](https://github.com/aaronpeikert/repro)[^repropackage]:

[^repropackage]: https://github.com/aaronpeikert/repro

@@

The [`repro`-package](https://github.com/aaronpeikert/repro) contains several helpers to work with reproducibility tools.
For example, it can check if you computer is set up to use the tools we rely on:

```{r}
check_make()
```

```{r}
check_docker()
```

If these commands detect that something is not installed or set up, they will give you detailed instructions (tailored to your operating system) on how to remedy the situation.
Follow the instructions, then rerun the command, till it tells you to not worry.

@@
